---
title: "Onboarding Otomoto PL - A/B Test Evaluation"
output: html_document
---

# ##############################################################################################################
# Retention analysis OKR1, OKR2                                                                                #
# Test users that did "home" vs users entered onboarding ("welcome_screen")                                    #
# use datasets created in `ret_any_D.R` and `ret_lead_D.R` files     
# Analysing longer period as I have more data available                                                        #
# ##############################################################################################################



```{r}
setwd("~/verticals-bi/scripts/r/3.Analysis/GVPI-160.OnboardingTestPL")
source("pop_suc_test.R")   #source functions needed to evaluate the test
```

# ################################################################################################
# OKR 1:
# Increase % of new users that return to the website after 7 days by 10%
# ################################################################################################


# ##############################################################################
# Mon 27 Nov - Sun 31 Dic 
```{r}
# First import pop_suc() function with specific period set
control <- pop_suc_okr1(df_any_ro, "2017-11-27", "2017-12-31", "rwd")
experiment <- pop_suc_okr1(df_any_ro_pwa, "2017-11-27", "2017-12-31", "rwd")
```


# Test dataset
```{r cars}
popA <- control$pop
popB <- experiment$pop
sucA <- control$suc
sucB <- experiment$suc

dfOnboarding <-
    data.frame(
        id = c("01", "02"),
        name = c("Original", "Variation with Onboarding"),
        period = c("2nd week", "2nd week"),
        PopulationMetric = c("new_users","new_users"),
        PopulationValue = c(popA, popB),
        SucessMetric = c("okr_1","okr_1"),
        SucessValue = c(sucA, sucB)
    )

dfOnboarding$ctr <- 
    dfOnboarding$SucessValue / dfOnboarding$PopulationValue
```

# Power analysis
```{r}
testResultsOnboarding <- 
    power.prop.test(
        n = dfOnboarding$PopulationValue, 
        p1 = dfOnboarding$ctr[1],
        p2 = dfOnboarding$ctr[2],
        sig.level = 0.05,
        alternative = "two.sided"
    )

testResultsOnboarding
```

Test is not significant, it doesn't have enough power to to detect a significant different
Difference is very tiny.
```{r}
(testResultsOnboarding$p2 - testResultsOnboarding$p1) / testResultsOnboarding$p1
```



# ################################################################################################
# OKR 2:
# Increase % of new users with 1+ reply after 14 days by 10%
# ################################################################################################


# ##############################################################################
# Mon 27 Nov - Sun 31 Dic 
```{r}
# First import pop_suc() function with specific period set
control <- pop_suc_okr2 (df_lead_ro, "2017-11-27", "2017-12-31", "rwd")
experiment <- pop_suc_okr2 (df_lead_ro_pwa, "2017-11-27", "2017-12-31", "rwd")
```


# Test dataset
```{r cars}
popA <- control$pop
popB <- experiment$pop
sucA <- control$suc
sucB <- experiment$suc

dfOnboarding <-
    data.frame(
        id = c("01", "02"),
        name = c("Original", "Variation with Onboarding"),
        period = c("2nd week", "2nd week"),
        PopulationMetric = c("new_users","new_users"),
        PopulationValue = c(popA, popB),
        SucessMetric = c("okr_2","okr_2"),
        SucessValue = c(sucA, sucB)
    )

dfOnboarding$ctr <- 
    dfOnboarding$SucessValue / dfOnboarding$PopulationValue
```

# Power analysis
```{r}
testResultsOnboarding <- 
    power.prop.test(
        n = dfOnboarding$PopulationValue, 
        p1 = dfOnboarding$ctr[1],
        p2 = dfOnboarding$ctr[2],
        sig.level = 0.05,
        alternative = "two.sided"
    )

testResultsOnboarding
```


Variation is -9% below original. Test has enough power.
```{r}
(testResultsOnboarding$p2 - testResultsOnboarding$p1) / testResultsOnboarding$p1
```


# #############################################################################
# Analyse OKR2 only on same day from 1st interaction
```{r}
# First import pop_suc() function with specific period set
control <- pop_suc_okr2_0 (df_lead_ro, "2017-11-27", "2017-12-31", "rwd")
experiment <- pop_suc_okr2_0 (df_lead_ro_pwa, "2017-11-27", "2017-12-31", "rwd")
```

# Test dataset
```{r cars}
popA <- control$pop
popB <- experiment$pop
sucA <- control$suc
sucB <- experiment$suc

dfOnboarding <-
    data.frame(
        id = c("01", "02"),
        name = c("Original", "Variation with Onboarding"),
        period = c("2nd week", "2nd week"),
        PopulationMetric = c("new_users","new_users"),
        PopulationValue = c(popA, popB),
        SucessMetric = c("okr_2_same_day","okr_2_same_day"),
        SucessValue = c(sucA, sucB)
    )

dfOnboarding$ctr <- 
    dfOnboarding$SucessValue / dfOnboarding$PopulationValue
```

# Power analysis
```{r}
testResultsOnboarding <- 
    power.prop.test(
        n = dfOnboarding$PopulationValue, 
        p1 = dfOnboarding$ctr[1],
        p2 = dfOnboarding$ctr[2],
        sig.level = 0.05,
        alternative = "two.sided"
    )

testResultsOnboarding
```

When considering only the same day, variation is - 15% below original. Test is significant.
```{r}
(testResultsOnboarding$p2 - testResultsOnboarding$p1) / testResultsOnboarding$p1
```

# Analyse OKR2 only on days 1-14 from 1st interaction (not considering same day)
```{r}
# First import pop_suc() function with specific period set
control <- pop_suc_okr2_1_14 (df_lead_ro, "2017-11-27", "2017-12-31", "rwd")
experiment <- pop_suc_okr2_1_14 (df_lead_ro_pwa, "2017-11-27", "2017-12-31", "rwd")
```

# Test dataset
```{r cars}
popA <- control$pop
popB <- experiment$pop
sucA <- control$suc
sucB <- experiment$suc

dfOnboarding <-
    data.frame(
        id = c("01", "02"),
        name = c("Original", "Variation with Onboarding"),
        period = c("2nd week", "2nd week"),
        PopulationMetric = c("new_users","new_users"),
        PopulationValue = c(popA, popB),
        SucessMetric = c("okr_2_1-14","okr_2_1-14"),
        SucessValue = c(sucA, sucB)
    )

dfOnboarding$ctr <- 
    dfOnboarding$SucessValue / dfOnboarding$PopulationValue
```

# Power analysis
```{r}
testResultsOnboarding <- 
    power.prop.test(
        n = dfOnboarding$PopulationValue, 
        p1 = dfOnboarding$ctr[1],
        p2 = dfOnboarding$ctr[2],
        sig.level = 0.05,
        alternative = "two.sided"
    )

testResultsOnboarding
```

When considering days 1 to 14, variation -0.5% below original (on dame day was -15%), tough test is not significant.
```{r}
(testResultsOnboarding$p2 - testResultsOnboarding$p1) / testResultsOnboarding$p1
```

