---
title: 'Feature Release: Save as a Draft'
output:
  pdf_document: default
  html_document:
    theme: spacelab
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Requested By (PM):**
Cláudia Rosado  
**Product:**  
Otomoto, Autovit, Standvirtual (desktop)  
**Feature:**  
Save as Draft (Button in Posting Flow)  
**Goal Description / User Behavior to Change:**  
"Understand if users are interested in "save ads as a draft" and check if having this option reduce the posting flow conversion rate."  
**Main Metric to Impact:**  
Posting Flow Convertion Rate (posting_add_click / posting_form)  
**Metric Goal to Achieve:**  
Don't decrease Posting Flow Convertion Rate  
**Expected Release Date:**  
  
**Effective Release Date:** 
  
**Related JIRA Ticket:**  
GVPI-117  

### **Conclusions**
This in not the final reports as it isn't finished. It's not finished because we cannot draw statistically relevant conclusions from the data that we have at current moment (11th/Oct - 24th/Oct). In this particular case, for all the countries (OTO, AUT, STV), we don't have the needed sample size with a statistical power greater than 0.8 (currently: OTO(0.2768531), AUT(0.2167030), STV(0.07786580)). 
The difference between "Original"(A)  and "Variation With Save Draft Button"(B) conversions rates is between -0.881 p.p. (-1.84%) in STV and +0.0141 (2.01%) in OTO.

As the differences between A and B are very small, we need a bigger sample (recommended samples: OTO(65188), AUT(16143), STV(50465)). These bigger samples would take the test to run for more 2 months.
Even then, **I my personal opinion/intuition**, we wouldn't see big differences.

Nevertheless, it's necessary to fix the "save draft" button's tracking before ending the test, as I would like to test another hyphothesis: people are savings drafts, abandoning the posting flow, recovery the ad in their personal account and posting it from there. 

### **Otomoto**
```{r , echo=FALSE}
library(pander)
library(knitr)
library(kableExtra)

df <- NULL

df <-
  data.frame(
  id = c("9010710728", "9009940388"),
  name = c("Original", "Variant with Button"),
  period = c("Oct 11, 2017 - Oct 24, 2017", "Oct 11, 2017 - Oct 24, 2017"),
  PopulationMetric = c("posting_form","posting_form"),
  PopulationValue = c(15538, 15543),
  SucessMetric = c("posting_add_click","posting_add_click"),
  SucessValue = c(10823, 10937)
  )

df$ctr <- 
  df$SucessValue / df$PopulationValue

testResults <- 
  power.prop.test(
    n = df$PopulationValue, 
    p1 = df$ctr[1],
    p2 = df$ctr[2],
    sig.level = 0.05,
    alternative = "two.sided"
  )

neededSample <- 
  power.prop.test(
    p1 = df$ctr[1],
    p2 = df$ctr[2],
    sig.level = 0.05,
    power = 0.8,
    alternative = "two.sided"
  )$n

otomotoData <- df
otomotoTestResults <- testResults
neededSampleOtomoto <- neededSample

knitr::kable(otomotoData, format = "html", padding = 2) %>%
  kable_styling

testResults

df <- NULL
testResults <- NULL
neededSample <- NULL
```

### **Autovit**
```{r , echo=FALSE}
library(pander)
library(knitr)
library(kableExtra)

df <- NULL

df <-
  data.frame(
  id = c("9024060291", "9010870766"),
  name = c("Original", "Variant with Button"),
  period = c("Oct 11, 2017 - Oct 24, 2017", "Oct 11, 2017 - Oct 24, 2017"),
  PopulationMetric = c("posting_form","posting_form"),
  PopulationValue = c(2848, 2658),
  SucessMetric = c("posting_add_click","posting_add_click"),
  SucessValue = c(2045, 1871)
  )

df$ctr <- 
  df$SucessValue / df$PopulationValue

testResults <- 
  power.prop.test(
    n = df$PopulationValue, 
    p1 = df$ctr[1],
    p2 = df$ctr[2],
    sig.level = 0.05,
    alternative = "two.sided"
  )

neededSample <- 
  power.prop.test(
    p1 = df$ctr[1],
    p2 = df$ctr[2],
    sig.level = 0.05,
    power = 0.8,
    alternative = "two.sided"
  )$n

autovitData <- df
autovitTestResults <- testResults
neededSampleAutovit<- neededSample

knitr::kable(autovitData, format = "html", padding = 2) %>%
  kable_styling

testResults

df <- NULL
testResults <- NULL
neededSample <- NULL
```

### **Standvirtual**
```{r , echo=FALSE}
library(pander)
library(knitr)
library(kableExtra)

df <- NULL

df <-
  data.frame(
  id = c("9031150194", "9016300173"),
  name = c("Original", "Variant with Button"),
  period = c("Oct 11, 2017 - Oct 24, 2017", "Oct 11, 2017 - Oct 24, 2017"),
  PopulationMetric = c("posting_form","posting_form"),
  PopulationValue = c(1878, 1925),
  SucessMetric = c("posting_add_click","posting_add_click"),
  SucessValue = c(881, 920)
  )

df$ctr <- 
  df$SucessValue / df$PopulationValue

testResults <- 
  power.prop.test(
    n = df$PopulationValue, 
    p1 = df$ctr[1],
    p2 = df$ctr[2],
    sig.level = 0.05,
    alternative = "two.sided"
  )

neededSample <- 
  power.prop.test(
    p1 = df$ctr[1],
    p2 = df$ctr[2],
    sig.level = 0.05,
    power = 0.8,
    alternative = "two.sided"
  )$n

stvData <- df
stvTestResults <- testResults
neededSampleSTV<- neededSample

knitr::kable(stvData, format = "html", padding = 2) %>%
  kable_styling

testResults

df <- NULL
testResults <- NULL
neededSample <- NULL
```